Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-24 cbm-rbd-paper.tex
policy section start

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
\def\eknow{e_k^{(\tnow)}}
\def\cknow{c_k^{(\tnow)}}
\def\vectknow{\vec{t}_k^{(\tnow)}}
\def\Phinow{\Phi^{(\tnow)}}
\newcommand{\gnow}{g^{(\tnow)}}

@@

\section{Dynamic maintenance policy based on the current system reliability function (RUL/RLD)}

To find the optimal moment for maintenance based on the current system reliability function $\Rsysnow(t)$,
we minimize the expected average cost per time unit,
called the unit cost rate, $g(\tau)$,
to find the cost-optimal moment of maintenance $\tau_*$
(could be discounted as well, out of scope here.)

We use the expected one-cycle cost rate 
\citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen}
to calculate the unit cost rate.
Although a different, renewal theory based way to calculate the unit cost rate is often used
in CBM literature \citep[e.g.,][]{2013:si-et-al,2011:kim-et-al},
%As we discussed in the Introduction,
we use the one-cycle cost rate as it is the most appropriate for our situation,
where $\tau_*$ changes with every cycle, and indeed changes with $\tnow$.
%since it considers only the costs with respect to the current cycle.

\subsection{Expected unit cycle cost rate}

Let $c_p$ be the cost of planned / preventive maintenance, and $c_u$ the cost of unplanned / breakdown maintenance, where $c_p < c_u$.
Usually, set-up costs, work costs and downtime costs are much higher for unplanned / breakdown maintenance,
such that often, $c_p \ll c_u$,
and these are exactly the situations where CBM is most effective (***cite working paper on relative benefit).

@@

>>>>

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
\def\eknow{e_k^{(\tnow)}}
\def\cknow{c_k^{(\tnow)}}
\def\vectknow{\vec{t}_k^{(\tnow)}}
\def\Phinow{\Phi^{(\tnow)}}
\newcommand{\gnow}{g^{(\tnow)}}
\newcommand{\tausnow}{\tau_*^{(\tnow)}}
\newcommand{\tsetup}{\tau_{\text{setup}}}

@@

\section{Dynamic/Adaptive maintenance policy based on the current system residual life distribution}
\label{sec:policy}

We can now derive the adaptive / dynamic maintenance policy
that resembles a CBM policy.
However, instead of a determining a threshold for a degradation signal like in usual CBM policies,
we determine, for each present time $\tnow$,
the adaptive and dynamic timespan $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time,
$\tausnow$ will typically decrease,
and whenever $\tausnow$ decreases below $\tsetup$, the timespan needed to set up maintenance work
(often referred to as setup time),
a preventive maintenance action is initiated.

The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
using the expected unit cost rate for the current operational cycle, see Section~\ref{sec:costrate} below.
Each operational cycle starts with the system being in an (as good as) new state,
i.e., all components in the system are new and have not aged.
A cycle ends when the system is either maintained preventively at $\tnow + \tausnow$ (on an absolute time scale),
or the system fails, which triggers a corrective maintenance action.
We assume that either maintenance action takes negligible time,
and that either action results in an (as good as) new system state by replacing all components,
such that the system begins a new cycle begins under identical conditions.

***info from finished cycle is added to component knowledge base,
thus included in $\nkz$ and $\ykz$ for the following cycle.

Therefore, at each present time $\tnow$
(at a frequency small enough to be negligible on the system lifetime scale),
the current residual life distribution $\Rsysnow(t)$ is recalculated,
and the corresponding $\tausnow$ determined.

***as $\Rsysnow(t)$ on discrete grid until horizon, optimize $\tausnow$ over same discrete grid.
if $\gnow(\tau)$ always decreasing, corrective maintenance strategy! so we can switch maintenance policy!

%To find the optimal moment for maintenance based on the current system reliability function $\Rsysnow(t)$,
%we minimize the expected average cost per time unit,
%called the unit cost rate, $g(\tau)$,
%leading to the cost-optimal moment of maintenance $\tau_*$.
%(could be discounted as well, out of scope here.)

\subsection{Expected unit cycle cost rate}
\label{sec:costrate}

We use the expected one-cycle cost rate 
\citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen}
to calculate the unit cost rate.
Although a different, renewal theory based way to calculate the unit cost rate is often used
in CBM literature \citep[e.g.,][]{2013:si-et-al,2011:kim-et-al},
%As we discussed in the Introduction,
we use the one-cycle cost rate as it is the most appropriate for our situation,
where $\tau_*$ changes with every cycle, and indeed changes with $\tnow$ within each cycle.
%since it considers only the costs with respect to the current cycle.

Let $c_p$ be the cost of planned (preventive) maintenance, and $c_u$ the cost of unplanned (breakdown) maintenance, where $c_p < c_u$.
Usually, set-up costs, work costs and downtime costs are much higher for unplanned / breakdown maintenance,
such that often, $c_p \ll c_u$,
and these are exactly the situations where CBM is most effective
(***cite de Jonge and Teunter working paper on relative benefit).

@@

***$\tsetup$ could vary over time, e.g., longer on weekends or outside office hours,
